What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Final tweaks. Final version?

We present a method for the automatic acquisition of a corpus of disputed claims from the web. We consider a claim to be disputed if a page on the web suggests that this claim is wrong and that other people believe it is true.

@@

We argue why such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.

@@

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. We use the word {\it claim} to mean a statement of opinion or fact contained in the text of a web page. 
We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and also that there are others that are making the claim. We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed claim.

We believe that this corpus or disputed claims will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approximately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particularly topical at particular times (Section~\ref{analysis}).

@@

The problem of determining information credibility on the web is becoming increasingly important. In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations. The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards. 
The web is very different. A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them. Moreover, the Internet has little in the way of publishing barriers or quality control. If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page looks how they expect a credible source to look; or they can check whether the information is consistent with information available from other sources.

@@

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{Adler2008b} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing. Some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user. These metrics do a good job at detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.

In our research, we are following a third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. 
Two instances of the same phrase may have the same sense, but a different reference, or two different phrases may refer to the same thing. 
For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times. ``The company is not going bust'' does not contract ``the company is doing great'' if the statements are about different companies.

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern. Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).

\begin{figure*}[tb]
\begin{center}
\begin{tabular}{|l|l|l|l|}
  \hline
  & {\bf extracted text} & {\bf valid} & {\bf details} \\
  \hline
  1. & the false claim that {\it won't go away} & no & ``wont go away'' is not a statement \\
  2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
  3. & falsely claimed that {\it federal labor laws do not apply} & no & object of the verb is not present\\
  4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
  5. & wrongly believe that {\it the moon is made of cheese} & yes & it is a statement about the world \\
\hline
\end{tabular}
\end{center}
\caption{We filter out text that does not look like a statement}
\label{filtered}

@@

This is an instance of pattern matching, a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type, Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed. Most often they construct the patterns automatically and often choose them on the basis of
statistics.

In this work we simply start with an initial set of manually crafted search patterns. We then identified additional patterns by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim and manually selected those patterns that made sense to us. This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class. This process is iterated several times and at each times a score is given to each extraction pattern and to each new lexicon entry and only the most reliable ones are retained. In our case, the semantic entity of interest are the claims. Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."

@@

Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates-fig}):

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it is plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``Some believe that Elvis is dead'' implies much more skepticism than ``I believe Elvis is dead''. 
 \end{itemize}

@@

\begin{figure}
\vspace{0.5cm}
 \begin{center}
  \begin{tabular}{|llll|}
\hline
{\bf accuracy}      & {\bf count}    &  {\bf percent}  & {\bf cummulative} \\
      \hline
dead on & 16   &   32\%  &   32\% \\
within 10 days & 9    &   18\%  &   50\% \\
within 30 days & 12   &   24\%  &   74\% \\
within 90 days & 3    &   6\%   &   80\% \\
within 1 year & 6    &   12\%  &   92\% \\ 
off by more than 1 year   & 4    &   8\%   &   100\% \\ 
\hline
  \end{tabular}
 \end{center}

@@

We use the Yahoo BOSS API~\cite{yahoo-boss} to search for occurrences of our patterns on the web. Using Yahoo BOSS allows us to search for patterns on a vast number of web pages, without having to build our own search engine. We search Yahoo BOSS for a raw string such as ``the misconception that'', download every page that Yahoo lists in its search results, and then look for text that matches any of our known patterns.

Since we are using an existing search engine, we are limited to searching for simple text strings. This requires us to generate multiple patterns that are almost the same, other than for synonyms, for example we have both ``the lie that'' vs ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.

@@

It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first). Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).

Knowing the rough date when someone believed or disputed something allows us te produce fuzzy time trends (Section~\ref{timetrends}). Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g. Elvis was alive in the past, but isn't not).

@@

Searching the web for our patterns yields a collection of strings. From this collection, we want to filter out any strings that are not making a falsifiable claim, and any strings that make a claim that is ambiguous.

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out. A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).

@@

Whether a claim is unambiguous can be highly subjective. For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''. When manually judging claims, we considered a claim to be unambiguous if an average person would be pretty sure what the claim meant without knowing its context.

We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

The {\it classifier accuracy} column in Figure~\ref{templates-fig} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g. 62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus, the pattern precision (e.g. 52\% for ``believe that'').

We can observe that the patterns in the ``something false'' group have much higher precision than the ``plausible to not believe it'' group, but have a lot less hits. Similarly, we can observe that our classifier performs much better on the ``something false'' patterns, with accuracy getting into the high seventies.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5.pdf}
	\caption{Frequency of each of the top nouns individually}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

\vspace{0.25cm}
\section{Using Disputed Claims}
\label{using}

@@

\vspace{0.25cm}
\section{Analyzing the Data}
\label{analysis}
\input{analysis.tex}

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analysed the distribution of noun frequencies in claims associated with January 10th of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even the nouns prove to be quite interesting.

@@

These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. They tracked highly repeated phrases, rather than nouns used in disputed claims. Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.

@@

Once we know what nouns are disputed, it is interesting to know what it is about a noun that is disputed. For example, what is it that people are disputing about ``Obama'' or ``Iraq''? To address this question, we took the set of claims that contained each popular noun (e.g. ``Obama'') and looked for sets of words that occurred together much more frequently than would be expected if claims were formed randomly. For example in our claims about ``Obama'', we found the word cluster ``health care'' because most claims about Obama that contain the word ``health'' also contain the word ``care'' and vice-versa.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting; for example many claims talk about the united states, even when that is not an important part of what is disputed.

In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning. This will allow us to better attack some of the problems we outlined in Section~\ref{using}.

@@

Creating a comprehensive corpus of disputed claims presents many challenges: how to create patterns, how to search for patterns, how to avoid malformed sentences, how to resolve or filter out ambiguous claims, how to determine if two claims are paraphrases, and how to determine if text on the web contains a claim that our database says is disputed. For each of these tasks, we have implemented enough to get useful results, but there is much scope to do things better.

@@

Our data set currently includes approximately 1.1 million records. We intend to expand this by several orders of magnitude.

>>>>

We present a method for the automatic acquisition of a corpus of disputed claims from the web. We consider a factual claim to be a {\it disputed claim} if a page on the web suggests both that the claim is false and also that other people say it is true.

@@

We argue that such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we report what our current corpus reveals about what is being disputed on the web.

@@

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. We use the word {\it claim} to mean a statement of opinion or fact contained in the text of a web page. 
We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and also that there are others who say the claim is true. We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we use. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed unambigous claim.

We believe that this corpus of disputed claims will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, creating visualization tools that let users know what is disputed about a topic that interests them, and building statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}). In Section~\ref{analysis} we show how our corpus can be used to reveal trends in dispute on the web.

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approximately 1.1 million strings that our classifier believes are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

The problem of determining information credibility on the web is becoming increasingly important. In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations. The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards. 
The web is very different. A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them. Moreover, the Internet has little in the way of publishing barriers or quality control. If a user is to extract reliable information from the web then they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page has features that they would expect a credible source to have; or they can check whether the information is consistent with information available from other sources.

@@

Researchers have identified a variety of metrics that can be used to automatically estimate the quality of a document based on looking at its content. For Wikipedia, Blumenstock~\cite{Blumenstock2008} estimates the quality of an article by the word count and WikiTrust~\cite{Adler2008b} identifies potentially unreliable sections of an article by analyzing its edit history. Custard and Sumner~\cite{Custard2005} use a combination of metrics to measure web site quality, including number of links and whether it contains videos. Fogg et al~\cite{Fogg2003} have shown that users commonly evaluate the credibility of a web site based on factors such as the design look, the information structure of the site, and the tone of the writing; some of the factors identified by Fogg et al could potentially be measured automatically and used to guide a user. These metrics do a good job at detecting pages that resemble pages that contain unreliable information, but they do not protect against authors who write untrustworthy information in the style of a trustworthy document.

In our research, we are following a third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to add disputed claims to the corpus manually, and by scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine whether this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. 
Two instances of the same phrase may have the same sense, but a different reference, or two different phrases may refer to the same thing. 
For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush; ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England; and ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}).  Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).

\begin{figure*}[tb]
\begin{center}
\begin{tabular}{|l|l|l|l|}
  \hline
  & {\bf extracted text} & {\bf valid} & {\bf details} \\
  \hline
  1. & the false claim that {\it won't go away} & no & ``wont go away'' is not a statement \\
  2. & falsely claimed that {\it he didn't do it} & no & ``he'' and ``it'' are unbound referents \\
  3. & falsely claimed that {\it federal labor laws do not apply} & no & ambiguous: apply to what?\\
  4. & false claim that {\it Elvis is alive} despite all evidence & yes & but drop everything after ``despite''\\
  5. & wrongly believe that {\it the moon is made of cheese} & yes & it is a statement about the world \\
\hline
\end{tabular}
\end{center}
\caption{We filter out text that does not look like a statement}
\label{filtered}

@@

This is an instance of pattern matching, a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for patterns such as ``$X$ such as $Y$'' to infer hyponyms; Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events; Caraballo~\cite{Caraballo2001} searched for patterns like ``$X$ and $Y$'' to find nouns of the same type; Girju et al~\cite{Girju2003} searched for patterns like ``$X$'s $Y$'' and ``$X$ of the $Y$'' to infer  metronyms; and TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These types of methods differ on how the patterns are generated and on how the extraction of the relevant information is performed. Most often they construct the patterns automatically and often choose them on the basis of
statistics.

In this work we simply start with an initial set of manually crafted search patterns. We then identified additional patterns by searching for the text of known disputed claims, observing what text commonly occurred as a prefix of a known disputed claim, and manually selected those patterns that made sense to us. This technique is inspired by bootstrapping algorithms~\cite{jones99bootstrapping,Girju2003,Snow2005} that start with a small number of seed words that belong to a semantic class of interest; these seed words are used to learn the extraction patterns that then can be used to extract new members of the same semantic class. In our case, the semantic entities of interest are the disputed claims. Currently, we {\em manually} choose the patterns and claims to retain, i.e., as oppose to most relevant work, we don't {\em learn} the patterns and we don't use a measure of "reliability."

@@

Not all patterns have the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates-fig}):

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it is plausible that someone else might not believe it. This is subtly different from the previous group. For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``Some believe that Elvis is dead'' implies much more skepticism than ``I believe Elvis is dead''. 
 \end{itemize}

@@

\begin{figure}
 \begin{center}
  \begin{tabular}{|llll|}
\hline
{\bf accuracy}      & {\bf count}    &  {\bf percent}  & {\bf cumulative} \\
      \hline
dead on & 16   &   32\%  &   32\% \\
within 10 days & 9    &   18\%  &   50\% \\
within 30 days & 12   &   24\%  &   74\% \\
within 90 days & 3    &   6\%   &   80\% \\
within 1 year & 6    &   12\%  &   92\% \\ 
off by more than 1 year   & 4    &   8\%   &   100\% \\ 
\hline
  \end{tabular}
 \end{center}

@@

We use the Yahoo BOSS API~\cite{yahoo-boss} to search for occurrences of our patterns on the web. Using Yahoo BOSS allows us to search for patterns on a vast number of web pages without having to build our own search engine. We search Yahoo BOSS for a raw string such as ``the misconception that'', download every page that Yahoo lists in its search results, and then look for text that matches any of our known patterns.

Since we are using a general purpose search engine, we are limited to searching for simple text strings. This requires us to generate multiple patterns that are almost the same, other than for synonyms, for example we have both ``the lie that'' vs ``the deceit that''. We are also restricted to searching for patterns that consist entirely of either a prefix or a suffix. For example we could not search for ``say that $S$ despite'', because there is no way to require that ``despite'' and ``say that'' be in the same sentence.

@@

It is useful to be able to update our corpus as new pages appear on the web without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}). We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

Knowing the rough date when someone believed or disputed something allows us to produce fuzzy time trends (Section~\ref{timetrends}). Moreover, it is important to know when people believed particular things, since things that were true in the past may not be true any more (e.g. Elvis was alive in the past, but isn't now).

@@

Searching the web for patterns yields a collection of strings. From this collection, we want to filter out any strings that are not making a falsifiable claim, and any strings that make a claim that is ambiguous.

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we want to filter some of them out. A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).

@@

Whether a claim is unambiguous is ofter subjective. For example, in the string ``Obama is the president'' it is possible that ``Obama'' is referring to someone other than ``Barack Obama'' and ``the president'' is referring to a position other than ``President of the United States''. When manually judging claims, we considered a claim to be unambiguous if an average person would be pretty sure what the claim meant without knowing its context.

We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and part-of-speech tag of the first and second words.

The {\it classifier accuracy} column in Figure~\ref{templates-fig} shows how accurately our classifier was able to determine whether any given string matched by a particular pattern is an unambiguous disputable claim. To provide a baseline for what these figures mean, consider that a random classifier would have 50\% accuracy, a classifier that always said ``yes'' would have accuracy equal to the pattern precision (e.g. 62\% for ``the myth that''), and a classifier that always said ``no'' would have accuracy equal to 100 minus the pattern precision (e.g. 52\% for ``believe that'').

We can observe that the patterns in the ``something false'' group have much higher precision than the ``plausible to not believe it'' group, but appear much less frequently on the web. Similarly, we can observe that our classifier performs much better on the ``something false'' patterns, with accuracy getting into the high seventies.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{images/2by5.pdf}
	\caption{Number of claims containing a particular noun on January 10th of any particular year}
	\label{multiplot_nouns}
	\end{center}
\end{figure*}

@@

\section{Using Disputed Claims}
\label{using}

@@

\section{Analyzing the Data}
\label{analysis}
\input{analysis.tex}

@@

Figure~\ref{multiplot_nouns} shows the frequency with which particular nouns were discussed in particular years. For example the claim ``Obama is a muslim'' contains the nouns ``Obama'' and ``Muslim''. We used the NLTK~\cite{Bird2009} part-of-speech tagger to identify the nouns found in each of our claims. We then analyzed the distribution of noun frequencies in claims made on January 10th of every year from 2000 to 2010. Although the date we searched for was in January, the claims we found are often from other points in the year, due to the fuzzy nature of our date search mechanism (Figure~\ref{dateaccuracy}). We excluded uninteresting nouns such as ``someone'', ``anybody'' and ``something'', and plotted graphs for the ten most disputed nouns (Figure~\ref{multiplot_nouns}). All graphs are plotted on the same scale. The y axis is the number of claims that contained the noun, and the x axis is the year in which the claim was made. It is likely that a Named Entity Recognition algorithm~\cite{Nadeau2007} would produce better results, but even these nouns prove to be quite interesting.

@@

These graphs are similar to those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. MemeTracker tracked highly repeated phrases, rather than nouns used in disputed claims. Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.

@@

Once we know what nouns are disputed, it is interesting to know what it is about a noun that is disputed. For example, what is it that people are disputing about ``Obama'' or ``Iraq''? To address this question, we took the set of claims that contained each popular noun (e.g. ``Obama'') and looked for sets of words that occurred together much more frequently than would be expected if claims were formed randomly. For example in our claims about ``Obama'', we found the word cluster ``health care'' because most claims about Obama that contain the word ``health'' also contain the word ``care'' and vice-versa. We used an agglomerative clustering algorithm to group together words that co-occur in the same claims.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words in the cluster. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see discussion about President Ahmadinejad's alledged statement that Israel should be wiped off the map (which the authors had not previously realized was a disputed). Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.

In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify text that is making a disputed claim. This will allow us to better attack some of the problems we outlined in Section~\ref{using}.

@@

Creating a comprehensive corpus of disputed claims presents many challenges: how to create patterns, how to search for patterns, how to avoid malformed sentences, how to resolve or filter out ambiguous claims, how to determine if two claims are paraphrases, and how to learn interesting things from the data set. For each of these tasks, we have implemented enough to get useful results, but there is much scope to do things better.

@@

Our data set currently includes approximately 1.1 million records. In the future we intend to expand this by several orders of magnitude.
